Learning to be wrong:

### 2021-02-27 manuscript/manuscript.Rmd
:pen:

Is this result merely an artifact of differing objectives?  @Gneiting2007's proper scoring rules are designed to select models which make the best forecast, and Model 2 really is the best choice for that task.  However, the adaptive management approach explicitly seeks to maximize expected utility, integrating over the uncertainty in the model, and yet it evolves away from Model 1 which would achieve that goal and settles on Model 2.  Note that this issue is not resolved by updating the learning step to reflect only the immediate reward -- it is in fact easy to see that so-called greedy algorithms would take the largest harvest possible and never reach the sustainable yield achieved by lower harvest rates of Model 1.

Perhaps Model 1 is a unicorn, a mythically simple model that gives optimal results but has no analogue in the real world.  This is not an easy assertion to prove either way.  Future observations consistently fall outside the 95% confidence intervals predicted under Model 1.  Unfortunately, such innaccurate predictions are only too common in the real world.  Have any of those led to effective policy despite the innnaccuracy?  Have any been replaced with more accurate models that have also driven worse decisions? That is more difficult to answer.  What this example demonstrates is that if such unicorn models exist, our current paradigm will surely filter them out eventually, to be replaced with worse outcomes.
<!-- Omit this?  Does it beg an example? -->
There is at least one technique which might address the problem presented here.  Recently developed techniques based on model-free deep reinforcement learning train multi-layer neural networks to approximate the optimal control policy without assuming or attempting to model the underlying dynamic process at all.  Feedback is based on cumulative reward, not short-term reward or predictive accuracy.

>>>>

Is this result merely an artifact of differing objectives?  @Gneiting2007's proper scoring rules are designed to select models which make the best forecast, and Model 2 really is the best choice for that task.  However, the adaptive management approach explicitly seeks to maximize expected utility, integrating over the uncertainty in the model, and yet it evolves away from Model 1 which would achieve that goal and settles on Model 2.  Note that this issue is not resolved by updating the learning step to reflect only the immediate reward -- it is in fact easy to see that so-called greedy algorithms would take the largest harvest possible and never reach the sustainable yield achieved by lower harvest rates of Model 1. To select Model 1 over alternatives like Model 2 which make better predictions but lead to worse outcomes requires a more long-term approach that forgoes iterative updating of probabilities as new data becomes available.  This is the opposite recommendation of _adaptive_ management  @Dietze2018

Perhaps Model 1 is a unicorn, a mythically simple model that gives optimal results but has no analogue in the real world.  This is not an easy assertion to prove either way.  Future observations consistently fall outside the 95% confidence intervals predicted under Model 1.  Unfortunately, such innaccurate predictions are only too common in the real world.  Have any of those led to effective policy despite the innnaccuracy?  Have any been replaced with more accurate models that have also driven worse decisions? That is more difficult to answer.  What this example demonstrates is that if such unicorn models exist, our current paradigm will surely filter them out eventually, to be replaced with worse outcomes.

<!-- Omit this?  Does it beg an example? -->
<!--
There is at least one technique which might address the problem presented here.  Recently developed techniques based on model-free deep reinforcement learning train multi-layer neural networks to approximate the optimal control policy without assuming or attempting to model the underlying dynamic process at all.  Feedback is based on cumulative reward, not short-term reward or predictive accuracy.  
-->
